Tabular Constraint Learning

### 2016-04-29 Paper/ECAI/tabular.tex
Edits part 2

@@

@@

\subsubsection*{Q2. How many redundant constraints are discovered?}
Our primary focus was accuracy, therefore we sometimes traded off less redundancy for more accuracy.
The motivation is that solutions can still be pruned using entailment or heuristics afterwards.
The constraints we considered to be redundant are either duplications (results that can be calculated in different ways, one of which seems superior) or constraints that hold by accident.
\tias{Advice, move to discussion}
Duplications should be detected in a post-processing step while accidental constraints should primarily be removed by adding data.

@@

\subsubsection*{Q3. How fast is the algorithm?}
\tias{Mention trade-off in the approach}
Concerning the speed of the algorithm we also prioritized accuracy when a trade-off had to be made.
For the 32 spreadsheets in the benchmark our implementation ran in $17.86s \pm 0.87s$.
The execution times vary widely though between spreadsheets, only four spreadsheets taking more than $0.2s$.
Most of the execution time in these cases goes towards searching either aggregate constraints or conditional aggregates.
The search for aggregates will be slow on spreadsheets containing larger groups of numeric data.
For conditional aggregates the number of candidate primary keys (all-different) and numeric vectors determines the running time (e.g. the case study example).

@@

\sergey{I think there should be three things: key example evaluated, benchmark of 30 spreadsheets and maybe the FBI example, how we can detect interesting dependencies and correct potential mistakes}

@@

@@

conclusions 
% points: 1) can be a base for an actual plugin or a function in excel 2) novel problem and challenge for systems and constraint solvers 3) can be part of the complicated pipeline togehter with the header detection
Our goal was to automatically identify constraints that hold in a spreadsheet.
We have presented and evaluated an approach that is able to learn a large set constraints from CSV data.

fututre work

>>>>

Generally \CSignature and / or the \CFunction can be relaxed to capture more constraints in the data, however, this also comes at a performance penalty. \samuel{More on this / example?}

@@

We examine three main questions concerning the accuracy, redundancy and efficiency of our approach, our main focus being accuracy.

@@

\subsubsection*{Q2. How many redundant constraints are discovered?}
Our primary focus was, as mentioned before, accuracy, therefore we sometimes traded off less redundancy for more accuracy.
The motivation is that solutions can still be pruned using entailment or heuristics afterwards.
The constraints we considered to be redundant are either duplications (results that can be calculated in different ways, one of which seems superior) or constraints that hold by accident.

@@

\subsubsection*{Q3. How fast is the algorithm?}
Concerning the speed of the algorithm we also prioritized accuracy when a trade-off had to be made.
For the 32 spreadsheets in the benchmark our implementation ran in $17.86s \pm 0.87s$.
The execution times vary widely though between spreadsheets, only four spreadsheets taking more than $0.2s$.
Most of the execution time in these cases goes towards searching either aggregate constraints or conditional aggregates.
The search for aggregates will be slow on spreadsheets containing larger groups of numeric data.
For conditional aggregates the number of candidate primary keys (all-different) and numeric vectors determines the running time (e.g. the case study example).

@@

\paragraph{Redundancy}
As mentioned before, there are two types of redundant constraints: duplications and accidental constraints.
Duplications should be detected throught in a post-processing step that uses entailment or heursitics to filter constraints.
Accidental constraints can sometimes be detected through heuristics, as well, however they can also be removed by adding additional data.

(\sergey{I think there should be three things: key example evaluated, benchmark of 30 spreadsheets and maybe the FBI example, how we can detect interesting dependencies and correct potential mistakes})

@@

\samuel{Two possible takes here: 1) recent interest in topics such as flashfill, etc -> sparked the idea for this project. This actually relates to constraint learning which has seen an uptick recently and is a subfield of long-established ILP. 2) ILP established field trying to learn structure / .., has been brought to the less traditional context (constraint learning), learning constraints / programs has been picked up by specific approaches such as flashfill etc which inspired this research}

@@

conclusions 
% points: 1) can be a base for an actual plugin or a function in excel 2) novel problem and challenge for systems and constraint solvers 3) can be part of the complicated pipeline togehter with the header detection
Our goal was to automatically identify constraints that hold in a spreadsheet.
We have presented and evaluated an approach that is able to learn a large set of constraints from CSV data.

\paragraph{Future work}
...
